FEM Model Analysis

### 2021-01-04 FEM_R/model_analysis.Rmd
Added more visualisations to model_analysis.Rmd and fixed problems created by rmarkdown update

---
title: "FEM Model Analysis"
output:
  html_document:
    df_print: paged
---

@@

  melted <- melt(combine, id.var = 'year', value.name = 'Prevalence')

@@

  cdMelted <- base %>%
                select(c('year', 'p_cancre_all', 'p_diabe_all', 'p_hearte_all')) %>%
                dplyr::rename('Cancer' = p_cancre_all, 'Diabetes' = p_diabe_all, 'Heart Disease' = p_hearte_all) %>%
                filter(year == 2012) %>%
                melt(id.var = 'year', value.name = 'Prevalence') %>%
                subset(select = -year)

@@

  # Extract vars, rename, and melt to put it in better format for graphing with ggplot2
  cdMelted <- base %>%
                select(c('year', 'p_cancre_all', 'p_diabe_all', 'p_hearte_all')) %>%
                dplyr::rename('Cancer' = p_cancre_all, 'Diabetes' = p_diabe_all, 'Heart Disease' = p_hearte_all) %>%
                melt(id.var='year', value.name = 'Prevalence')

@@

  ageMelt <- base %>%
              select(c('year', a5564, a6574, a7584, a85p)) %>%
              dplyr::rename('55 to 64' = a5564, '65 to 74' = a6574, '75 to 64' = a7584, '85+' = a85p) %>%
              melt(id.var = 'year', value.name = 'Prevalence')

>>>>

---
title: "FEM Model Analysis"
output: html_notebook
---

@@

  melted <- reshape2::melt(combine, id.var = 'year', value.name = 'Prevalence')

@@

  cdMelted <- base %>%
                select(c('year', 'p_cancre_all', 'p_diabe_all', 'p_hearte_all')) %>%
                dplyr::rename('Cancer' = p_cancre_all, 'Diabetes' = p_diabe_all, 'Heart Disease' = p_hearte_all) %>%
                filter(year == 2012) %>%
                reshape2::melt(id.var = 'year', value.name = 'Prevalence') %>%
                subset(select = -year)

@@

  # Extract vars, rename, and melt to put it in better format for graphing with ggplot2
  cdMelted <- base %>%
                select(c('year', 'p_cancre_all', 'p_diabe_all', 'p_hearte_all')) %>%
                dplyr::rename('Cancer' = p_cancre_all, 'Diabetes' = p_diabe_all, 'Heart Disease' = p_hearte_all) %>%
                reshape2::melt(id.var='year', value.name = 'Prevalence')

@@

  ageMelt <- base %>%
              select(c('year', a5564, a6574, a7584, a85p)) %>%
              dplyr::rename('55 to 64' = a5564, '65 to 74' = a6574, '75 to 64' = a7584, '85+' = a85p) %>%
              reshape2::melt(id.var = 'year', value.name = 'Prevalence')
